Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-19 ICML2019/main.tex
Reducing formulas.

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix III)

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
\begin{align*}
&\lapmechPr{\dataobs}{
\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
} = 0.19673467014,\\
&\lapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
\end{aligned}
  } = 0.11932560927,\\
&\lapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
  \end{aligned}
} = 0.07237464051.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
\begin{align*}
&\ilapmechPr{\dataobs}{
\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
&\ilapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
  \end{aligned}
} = 0.116272079,\\
&\ilapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
    \end{aligned}
} = 0.04277411.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
\begin{lem}
\label{lem_acc_hexp}
  In Beta-binomial model,
  we have following accuracy bound for this mechanism:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
  & \text{ where } c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}
\end{lem}

@@

By solving following equations:
  \[
  \frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
  \[
  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
   = 0.119325609\ or\ 0.116272079
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
  \[
\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
     = 0.072374641\ or\ 0.042774107
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
%The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
%\[
%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
%\]
By the triangle inequality of Hellinger distance, the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to $\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$.
Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
%\end{split}
\begin{align*}
LS(\dataobs)
& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
\left|~
\begin{aligned}
&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{aligned}
\right|\\
  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
\end{align*}

>>>>

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\todo{Is it correct
$\lapmechPr{\dataobs}{\ldots}$? }
\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix III)

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
\todo{What is the value of $\varepsilon$?}
%\begin{align*}
%&\lapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
%} = 0.19673467014,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%\end{aligned}
%  } = 0.11932560927,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
%  \end{aligned}
%} = 0.07237464051.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\lapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.19673467014 & t = 0\\
0.11932560927 & t = 1\\
0.07237464051 & t = 2
\end{cases}.
\end{align*}

@@

Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
\todo{
What is the value of $\varepsilon$?
Do we have the formula
\[
\ilapmechPr{\dataobs}{\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}?
\]
}
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%  \end{aligned}
%} = 0.116272079,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
%    \end{aligned}
%} = 0.04277411.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\ilapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.31606027941 & t = 0\\
0.11627207896 & t = 1\\
0.04277410743 & t = 2
\end{cases}.
\end{align*}

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
\begin{lem}
\label{lem_acc_hexp}
  In Beta-binomial model,
  we have following accuracy bound for this mechanism:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(t)  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}
\end{lem}

@@

By solving following equations:
%  \[
  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
\begin{align*}
 &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
 & = 0.19673467 \text{ or } 0.316060279
\end{align*}
%  \]
%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
%  \[
%  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
\begin{align*}
  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
  &= 0.119325609 \text{ or } 0.116272079
\end{align*}
%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
%  \[
%\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
%    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%    \cdot
%    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
%    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
\begin{align*}
 &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
 &=0.072374641 \text{ or }  0.042774107
%\]
\end{align*}
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
%The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
%\[
%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
%\]
By the triangle inequality of Hellinger distance,
the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\todo{
Do we need the experimental on this formula?
It is proved mathematically by case analysis.
For any $r \in \mathcal{R}$, we have
\begin{align*}
&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
& = 
\begin{cases}
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive}\\
\hellinger(\bysinfer(\dataobs') - \hellinger(\bysinfer(\dataobs), r)& \text{negative}
\end{cases}\\
& \leq 
\begin{cases}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
\end{cases}\\
&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{align*}
I think it would be a proposition.
}
%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
%\end{split}
%\begin{align*}
%LS(\dataobs)
%& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\left|~
%\begin{aligned}
%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
%\end{aligned}
%\right|\\
%  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
%\end{align*}
